Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2020-12-04 manuscript.tex
Correct silly copy-paste error [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/97ba541fc6e8ecf4377d084b5c11bb26604f334f.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/97ba541fc6e8ecf4377d084b5c11bb26604f334f/checks
https://github.com/habi/acinar-analysis-manuscript/runs/400847260

\emph{A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/786681} and has been submitted to the \href{https://journals.physiology.org/journal/ajplung}{\emph{American Journal of Physiology - Lung Cellular and Molecular Physiology}}}.
\emph{This version of the manuscript \href{https://github.com/habi/acinar-analysis-manuscript/commit/c56a516d2a7b3c0eec6f0b820c5d8744313bc31b...92c2e0a7eb9644d7f7c9527d87f520aaeaefc17f}{has been updated} since the original submission}.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/92c2e0a7eb9644d7f7c9527d87f520aaeaefc17f/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/92c2e0a7eb9644d7f7c9527d87f520aaeaefc17f}{habi/acinar-analysis-manuscript@92c2e0a}
on December 4, 2020.

>>>>

\emph{A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/786681} and has been submitted to the \href{https://journals.physiology.org/journal/ajplung}{\emph{American Journal of Physiology - Lung Cellular and Molecular Physiology}}}.
\emph{This version of the manuscript \href{https://github.com/habi/acinar-analysis-manuscript/commit/c56a516d2a7b3c0eec6f0b820c5d8744313bc31b...97ba541fc6e8ecf4377d084b5c11bb26604f334f}{has been updated} since the original submission}.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/97ba541fc6e8ecf4377d084b5c11bb26604f334f/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/97ba541fc6e8ecf4377d084b5c11bb26604f334f}{habi/acinar-analysis-manuscript@97ba541}
on December 4, 2020.
